---
title: "Plotting Indomethacin concentration"
output:
  html_notebook:
    css: style.css
---

### Lattice introduction

```{r}
suppressWarnings(library(lattice))
```

Let us load a dataset - Indometh. Indomethacin is a nonsteroidal anti-inflammatory drug (NSAID) commonly used as a prescription medication to reduce fever, pain, stiffness, and swelling from inflammation.

<img src="https://upload.wikimedia.org/wikipedia/commons/4/4e/Indometacin.svg" width="50%">


```{r}
data(Indometh)
df <- Indometh
head(df)
```

### Concentration vs time plotting

```{r}
xyplot(conc ~ time, data = df, type = "p",
       xlab = "Time (hours)", ylab = "Concentration (mcg/ml)",
       main = "Concentration vs. Time")

```
### Let us now visualize it separately for each subject.

```{r}
xyplot(conc ~ time | factor(Subject, levels = 1:6), data = df, type = "p",
       xlab = "Time (hours)", ylab = "Concentration (mcg/ml)",
       main = "Concentration vs. Time by Subject (Ordered)")

```

### Now let us look at superimposed trend lines.

```{r}
xyplot(conc ~ time, data = df, groups = Subject, type = "l",
       xlab = "Time (hours)", ylab = "Concentration (mcg/ml)",
       main = "Superimposed Concentrations by Subject",
       auto.key = list(space = "right"))
# auto.key = list(space = "right")) - adds legend to the right
```

## We are interested in finding out differences in the plasma concentration of Indomethicin amongst the six subjects.

```{r}
bwplot(~ conc | Subject, data = df,
       xlab = "Concentration (mcg/ml)", ylab = "Subject",
       main = "Boxplot of Concentrations by Subject",
       par.settings = list(
         box.rectangle = list(col = "darkgreen", lty = 1),
         plot.symbol = list(col = "red", pch = 16),
         superpose.symbol = list(col = "blue", pch = 20)
       ),
       horizontal = TRUE,
       layout = c(6, 1)
       )  

```

